\documentclass[conference]{IEEEtran}
\title{Mitigating DDoS attacks in Named Data Networking}%:\\ Cache/Content Poisoning}
\author{anonymous}

\usepackage{graphicx}
% \usepackage[colorlinks]{hyperref}
\usepackage[]{hyperref}
\usepackage{breakurl}
\usepackage{url}
\usepackage[nocompress]{cite}
% \usepackage{verbatim}
% \usepackage{algpseudocode}
\usepackage{algorithm}
\usepackage{algpseudocode}

\newcommand{\note}[1]{\vspace{2 mm}\par \noindent \textsc{Note}
\framebox{\begin{minipage}[c]{0.40 \textwidth}
\tt #1 \end{minipage}}\vspace{5 mm}\par}

\newcommand{\todo}[1]{\vspace{2 mm}\par \noindent \textsc{ToDo}
\framebox{\begin{minipage}[c]{0.42 \textwidth}
\tt #1 \end{minipage}}\vspace{5 mm}\par}

\begin{document}
\maketitle

\begin{abstract}
%
Distributed Denial of Service attack is a major problem on the existing Internet.
Named Data Networking (NDN) is a future Internet architecture that makes most existing DDoS attack infeasible.
At the same, NDN may be vulnerable to NDN-specific attacks, such as Interest flooding attack. 
This paper presents a simulation-based study on effects of Interset flooding DDoS attack, as well as study of a number of DDoS-attack prevention algorithms that can be implemented on NDN routers.
The presented results give evidences that flooding-based attacks have much less effective in NDN than in the current Internet, as well as that inherent flow-balance property of NDN (i.e., one Interests brings at most one Data) can be used as a basis for effective DDoS mitigation algorithms. 
%
\end{abstract}

\noindent {\bf Keywords:} Future Internet Architectures;
Content-Centric Networks; Information-Centric Networks, Named-data
Networking; Security; Denial-of-Service; Distributed
Denial-of-Service.

\input{intro.tex}

\section{ CCN Overview\label{ccn-intro}}

\section { DDoS Attacks in CCN \label{ccn-ddos}}
Brief overview of possible attacks in CCN, and scope of what we will tackle in this paper (Interest flooding).

\section { Interest Flooding in CCN }

\section {Countermeasures against Interest flooding}

Basic limits, probablity based on statistics, and dynamic window adjustment

(Description of each of the above, and their implications) 

\section {Evaluation}
\todo{Both simulation, as well as emulation for various sized topologies (trees as well as real topologies), various parameters etc.
List all possible parameters, say clearly which ones we vary, and which ones we do not, along with explanations.

Metrics that we will consider in our evaluation (Satisfaction rate for good clients, Link utilization near producers, Latency for good clients, good versus bad interests as a function of time).}

We want to explore the effectiveness of designed mitigation techniques in a two distinctive ways. First, we need to understand how each method works on a very ground level of a just few nodes and links. Second, we want to pick promising techniques and see if they work in a large scale networks of hundreds and thousands of nodes. To ensure the correct transition from small scale experiments to large scale experiments we had to use the same evaluation tool in order to eliminate any possibility of implementation discrepancy. As of today the only network simulator supporting full NDN logic is the NS-3 based ndnSIM software. 

\input{simulation-emulation.tex}


\subsection{Results from probability based on statistics}

\subsection{Results from dynamic window adjustment}

\input{large-scale.tex}

\section{Implications/Analysis}
Lessons we learnt, comparison of different mitigation techniques. 
Adapting these to mitigate other DDoS attacks.

\section{Conclusions and Future Work}

\bibliographystyle{plain}
\bibliography{references}

\appendix

\input{algos/physical-limits.tex}

\input{algos/fair-queueing.tex}

\input{algos/dynamic-limits.tex}

\input{algos/probabilistic.tex}

\input{algos/stats.tex}




\end{document}
